COSC-373 Final Report: Bitcoin

### 2022-05-12 paper/paper.tex
Fix wording.

A \emph{cryptographic hash function} is a hash function that takes as input data
(i.e., a \emph{message}) of an arbitrary size and outputs a bit array (i.e.,
\emph{hash}) of a fixed size. In the case of the SHA256 cryptographic hash
function, the hash has a length of 256 bits.

>>>>

A \emph{cryptographic hash function} is a hash function that takes as input data
of an arbitrary size, known as the \emph{message}, and outputs a bit array of a
fixed size, known as the \emph{hash}. In the case of the SHA256 cryptographic
hash function, the hash has a length of 256 bits.
